Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-08 thesis/chapters/ch_chapter3.tex
adding third chapter - individual metals paper

%mm substantive changes marked like this, others made silently

\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\shorttitle{Differential Metal Mixing}

\begin{document}

\title{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source}

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Benoit C{\^o}t{\'e}}
\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
\author{Kathryn V. Johnston}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\author{Brian W. O'Shea}
\affiliation{Department of Computational Mathematics, Science, and Engineering, Michigan State University, East Lansing, MI, 48824, USA}
\affiliation{Department of Physics and Astronomy, Michigan State University, East Lansing, MI, 48824, USA}
\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI, 48824, USA}
\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution. The PDF properties vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is predominately log-normal. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (e.g. N and Ba) mix less efficiently than elements dominated by supernova enrichment (e.g. $\alpha$ elements and Fe). This result is driven by the differences in source energetics and source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas. Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but over 20\% of metals dominated by AGB enrichment are retained. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

\keywords{}

@@

One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}. While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging. More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects. How to properly account for multi-phase mixing, however, is still poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Armillotta2018, Escala2018, Rennehan2018} 
% KVJ: citations to high-redshift work in this area
%\textbf{
and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
%}
Detailed hydrodynamics simulations incorporating a multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.

@@

In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}. The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

@@

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{species_bar}\\
\includegraphics[width=0.99\linewidth]{species_bar_ISM}
\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars. Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals.}
\label{fig:species_fractions}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{species_bar_sources}\\
\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model. These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{SE_density}\\
\includegraphics[width=0.95\linewidth]{SE_z}
\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
\label{fig:spatial distribution}
\end{figure}

@@

The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time. In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}. In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}. Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}. It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}. This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures .

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution}
\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation. The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
\label{fig:phase-statistics}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0}
\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation. We only show a sample of some of the elements dominated most by AGB enrichment at late times. The horizontal line marks a 50\% contribution.}
\label{fig:agb evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance}
\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}

@@

\acknowledgments
A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was partly funded by NASA  grant NNX14AP27G and by NSF grant AST18-15461. B.C. acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A. n. 724560) and from the National Science Foundation (USA) under grant No. PHY-1430152 (JINA Center for the Evolution of the Elements). B.W.O was supported in part by NSF grants PHY-1430152 and AST-1514700, by NASA grants NNX12AC98G, and NNX15AP39G, and by Hubble Theory Grant HST-AR-14315.001-A. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
\software{Numpy, Enzo, yt, astropy}

\bibliographystyle{yahapj}
\bibliography{msbib}

\appendix
\renewcommand\thefigure{\thesection.\arabic{figure}}
\setcounter{figure}{0}

@@

\begin{figure}
\centering
\includegraphics[width=0.475\linewidth]{density_PDF}
\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr. The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
\label{fig:density_pdf}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study}
\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases. Compare to Figure~\ref{fig:phase-statistics}.}
\label{fig:resolution-phase}
\end{figure*}

\end{document}

>>>>

\chapter[Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source]{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source \label{ch:chapter3}}
\let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2018b}}

%
% Copy paste paper here, without abstract or keywords
%

%\begin{abstract}
%Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
%stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution. The PDF properties vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is predominately log-normal. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (e.g. N and Ba) mix less efficiently than elements dominated by supernova enrichment (e.g. $\alpha$ elements and Fe). This result is driven by the differences in source energetics and source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas. Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but over 20\% of metals dominated by AGB enrichment are retained. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
%\end{abstract}

%\section*{Acknowledgments}

@@

One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017a,Andrews2017}. While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging. More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects. How to properly account for multi-phase mixing, however, is still poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Armillotta2018, Escala2018, Rennehan2018} 
% KVJ: citations to high-redshift work in this area
%\textbf{
and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
%}
Detailed hydrodynamics simulations incorporating a multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.

@@

In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}. The simulation discussed here was introduced in detail in \cite{Emerick2019} (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

@@

\begin{figure*}
\centering
\includegraphics[width=0.99\linewidth]{figures/ch3/species_bar}\\
\includegraphics[width=0.99\linewidth]{figures/ch3/species_bar_ISM}
\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars. Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals.}
\label{fig:species_fractions}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/species_bar_sources}\\
\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model. These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/SE_density}\\
\includegraphics[width=0.95\linewidth]{figures/ch3/SE_z}
\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
\label{fig:spatial distribution}
\end{figure}

@@

The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time. In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}. In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}. Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HWM2012}. It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}. This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures .

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/DD0390_element_by_element}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/O_Ba_distribution_evolution}
\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation. The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
\label{fig:phase-statistics}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/Half_AGB_Fraction_elements_s0}
\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation. We only show a sample of some of the elements dominated most by AGB enrichment at late times. The horizontal line marks a 50\% contribution.}
\label{fig:agb evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/stellar_CNM_distance}
\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}

@@

\section*{Acknowledgements}
A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was partly funded by NASA  grant NNX14AP27G and by NSF grant AST18-15461. B.C. acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A. n. 724560) and from the National Science Foundation (USA) under grant No. PHY-1430152 (JINA Center for the Evolution of the Elements). B.W.O was supported in part by NSF grants PHY-1430152 and AST-1514700, by NASA grants NNX12AC98G, and NNX15AP39G, and by Hubble Theory Grant HST-AR-14315.001-A. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

%\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
%\software{Numpy, Enzo, yt, astropy}

%\bibliographystyle{yahapj}
%\bibliography{msbib}

%************* APPENDICES ************************%

%\clearpage
%\appendix
\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}

@@

\begin{figure}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch3/density_PDF}
\includegraphics[width=0.475\linewidth]{figures/ch3/density_PDF_volume_weighted}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr. The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
\label{fig:density_pdf}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch3/O_Ba_resolution_study}
\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases. Compare to Figure~\ref{fig:phase-statistics}.}
\label{fig:resolution-phase}
\end{figure*}

\renewcommand\thesection{\thechapter.\arabic{section}}
